Code to reproduce results in _Semi-parametric generalized linear model for

### 2022-03-08 ManuscriptCode/Manuscript.Rmd
Add binomial fit

```{r AnalyzeOne}
run_analysis <- function(dat, cs_predict=5){
  #GEE
  dat_long <- unwrap(dat)
  res_gee <- geeglm(Resp ~ X1 + X2, data=dat_long, id = ID, family=binomial,
                 corstr = "exch")
  #Beta-binomial
  res_bb <- vgam(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                 data=dat, family =  betabinomial(lmu="logitlink"))
  #SPGLM
  op <- options(warn=-1)
  res_spglm <- spglm(cbind(NResp, ClusterSize - NResp) ~ X1 + X2, data=dat,
                   weights  = Freq)
  options(op)

@@

@@

  nms <- names(coef(res_spglm))
  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    BB = tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2]),
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE= sqrt(diag(vcov(res_spglm)))),
    .id = "Model")

  fit <- bind_rows(fit_bb, fit_spglm) %>%
    mutate(Type = "PDF")

>>>>

```{r AnalyzeOne}
run_analysis <- function(dat, cs_predict=5){
  #GEE
  dat_long <- unwrap(dat)
  res_gee <- geeglm(Resp ~ X1 + X2, data=dat_long, id = ID, family=binomial,
                 corstr = "exch")
  #Beta-binomial
  res_bb <- vgam(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                 data=dat, family =  betabinomial(lmu="logitlink"))
  #Binomial
  res_bin <- glm(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                 data=dat, family =  binomial)

  #SPGLM
  op <- options(warn=-1)
  res_spglm <- spglm(cbind(NResp, ClusterSize - NResp) ~ X1 + X2, data=dat,
                   weights  = Freq)
  options(op)

@@

   # binomial
  mns <- predict(res_bin, type="response", newdata=newd)

  fit_bin <- newd %>% 
    crossing(NResp=0:cs_predict) %>%
    mutate(ClusterSize = cs_predict,
           Prob = dbinom(NResp, size=cs_predict, prob=mns)) %>%
  mutate(Model="Bin")

@@

  nms <- names(coef(res_spglm))
  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    BB = tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2]),
    Bin = tibble(Term = nms,
                 Est = coef(res_bin),
                 SE = sqrt(diag(vcov(res_bin)))),
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE= sqrt(diag(vcov(res_spglm)))),
    .id = "Model")

  fit <- bind_rows(fit_bb, fit_bin, fit_spglm) %>%
    mutate(Type = "PDF")
